\documentclass[line, margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{enumitem} % Using to change spacing on lists
\usepackage{showframe}
\usepackage{fancyhdr} % Using to edit header/footer
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
\fancypagestyle{plain}{
    \fancyhf{}
    \rfoot{Compiled on {\ddmmyyyydate\today} at \currenttime}
    %\lfoot{Page \thepage}
    \renewcommand{\headrulewidth}{0pt}}
\pagestyle{plain}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Joseph Marvin McGee} % Your name at the top
\moveleft.5\hoffset\centerline{313 J Street} % Your address
\moveleft.5\hoffset\centerline{Davis, CA 90043}
\moveleft.5\hoffset\centerline{(323) 557-8647}
\moveleft.5\hoffset\centerline{email:jmmcgee@ucdavis.edu}

\begin{resume}
%---------------------------------------------------------------------------------------------------


\section{OBJECTIVE}
    Seeking a career that will help me take full advantage of my passion and experience in software engineering and computer science. 

\section{EDUCATION}
    {\sl Bachelor of Computer Science and Engineering}, (expected June 2016) \\University of California, Davis, Callifornia

\section{TECHNOLOGY \\ SKILLS} 
    {\sl Programming Languages:}  C, C++, Java, JavaScript, Python \\
    {\sl Web Technologies:} Django, Vaadin, NodeJS, JQuery \\
    {\sl Software Engineering:} Git, Maven, GNU Make \\
    {\sl Software:} Visual Studio, Vim, VirtualBox, MinGW, LaTeX, PostgreSQL \\
    {\sl Misc. Technologies:} bash, ssh, cron \\
    {\sl Operating Systems:} Debian-based Linux Distributions, Windows

\section{EXPERIENCE}
 {\bf Software Engineer (Intern)}, Intel / Hillsboro, OR
 \hfill {\bf 06/14 - 09/14}
 \begin{itemize}[noitemsep,nolistsep] \itemsep -2pt
     \item I was responsible for the design, development, configuration, and deployment of a database solution intended to allow the HPE Team to store and retrieve run information and the data associated with it more conveniently and systematically. (I designed and created a database-centered web application.)
 \end{itemize}

{\bf Student Manager}, University of California / Davis CA
\hfill {\bf 10/13 ---}
\begin{itemize}[noitemsep,nolistsep] \itemsep -2pt % Reduce space between items
    \item I am a Student Manager at the Engineering Student Start-up Center. My duties include supervising ESSC's space, managing its equipment, and planning and running events for the ESSC.
\end{itemize}

{\bf Co-Founder and Software Engineer}, Archer / Davis, CA
\hfill {\bf 05/13 ---}
\begin{itemize}[noitemsep,nolistsep] \itemsep -2pt % Reduce space between items
    \item I am one of two co-founders of a startup company, Archer, developing new input methods to smart TVs and set-top boxes.
    \item We recently incorporated and are developing our prototype and showing it to potential investors.
    \item I am responsible for is designing, coding and testing the prototype.
\end{itemize}

{\bf Teacher}, Educating Young Minds / Los Angeles, CA
\hfill {\bf 06/13 - 08/13} \\
{\bf Teacher}, Educating Young Minds / Los Angeles, CA
\hfill {\bf 06/12 - 08/12}
\begin{itemize}[noitemsep,nolistsep] \itemsep -2pt % Reduce space between items
\item
I taught grammar and mathematics to different classes of students ranging from 5th-12th grade.
\end{itemize}

{\bf Camp Counselor} Jenesse, Women's Shelter / Los Angeles
\hfill {\bf 07/11 - 08/11}
\begin{itemize}[noitemsep,nolistsep] \itemsep -2pt % Reduce space between items
\item 
\end{itemize}

%\section{COMMUNITY \\ SERVICE}

%Helped run the Race Against Violence for the last three years. This race raises money for the victims of domestic violence in Georgia. \\
%Helped construct a home and deck for the Goshen Valley Boy's Ranch.
%Cleaned and maintained the trails of Kennesaw Mountain as a repeating event on the second Saturday of every month.


\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

Member, Black Engineers Association \\
Member, Computer Science Club \\
Member, Linda Francis Alexander Scholars \\
 

%---------------------------------------------------------------------------------------------------

\end{resume}
\end{document}