\documentclass[10pt, letterpaper]{res}

%\usepackage[hmargin=2.00cm, vmargin=0.90cm]{geometry}
\usepackage[letterpaper, total={7in,10in}, hoffset=0.25in]{geometry}
%\usepackage[a4paper, total={8in,11in}]{geometry}
\usepackage{helvet}
%\usepackage{showframe}
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
\usepackage{enumitem}
\usepackage{tabularx}

\newcommand{\experience}[4]{
	{\bf #1}, #2 \hfill {\bf #3}
	\begin{itemize}[noitemsep]
		#4
    \end{itemize}
	%\vspace{-2mm}
}

\newcommand{\project}[4]{
	{\bf #1} \hfill {\bf #3} \vspace{-1mm} \\
	{\footnotesize #2}
	\begin{itemize}[noitemsep]
		#4
    \end{itemize}
	%\vspace{-2mm}
}


\begin{document}
\name{Joseph Marvin McGee}
\address{jmmcgee@ucdavis.edu | (323) 557-8647}

\begin{resume}
%---------------------------------------------------------------------------------------------------

%\section{OBJECTIVE}
%    Seeking a career that will help me take full advantage of my passion and experience in software engineering and computer science.

\section{EDUCATION}
    {\sl Master of Computer Science}, (expected June 2018) \hfill  Cumulative GPA: \quad 3.925/4.000 \\
    {\sl Bachelor of Computer Science and Engineering}, June 2016 \\
    University of California, Davis

\section{EXPERIENCE}
	\experience{Teacher's Assistant}{University of California, Davis}{}{
		\item[] FQ2016 ECS 132: Prob \& Sta in CS \hfill {\bf 09/16 --\footnotesize Present}
		\item[] SQ2016 ECS 030: Introduction to Programming (in C) \hfill {\bf 03/16 -- 06/16}
		\item[] SQ2015 ECS 122A: Algorithm Analysis and Design \hfill {\bf 03/15 -- 06/15}
	}

    \experience{Software Engineer}{Intel}{06/15 -- 09/15}{
		\item Modified OpenMPI to route network I/O through DPDK framework.
		\item Debugged OpenMPI and DPDK-based TCP/IP user-space network stacks to diagnose errors.
		\item Implemented deficiencies in DPDK-based TCP/IP network stacks to make them compatible with OpenMPI.
		\item Diagnosed and resolved linkage errors resulting from the interaction of several layers of shared/static libraries.
    }

    \experience{Software Engineer}{Intel}{06/14 -- 09/14}{
		\item Interpreted broad project requirements to create specific designs.
		\item Developed a database-centered web application to store automated testing data.
    }

	\experience{Student Manager}{Engineering Student Startup Center}{10/13 -- 03/15}{
		\item Created simple scripts to manage event-scheduling and forms management.
		\item Assisted students with equipment: 3D Printer, 3D Scanner, ShopBot.
		\item Planned and facilitated events; Coordinated with student-run organizations.
    }

	\experience{Software Engineer}{Archer}{05/13 --\footnotesize Present}{
		\item Design and develop prototype computer vision algorithms
		\item Design computer vision algorithms to facilitate a spatial input mechanism.
		\item Engineer prototype under time-pressure to show progress to potential investors.
		\item Design and debugged systems to visualize and quantify correctness of algorithm output.
	}

\section{PROJECTS}
    \project{Student Research}{University of California, Davis}{09/15 --\footnotesize Present}{
		\item Integrate DPDK into OpenMPI communication subsystem to characterize potential performance benefits
        \item Analyze bottlenecks in utilizing 10/40/100Gb network speeds on commodity hardware/software
        \item Explore extensible and flexible solution to scale to increasing core-counts and network speeds
	}

	\project{Fort Nitta: An Atari Rampart Remake}{ECS 160: Software Engineering}{01/15 -- 03/15}{
        \item Designed specification for multi-player network protocol--running over TCP/IP.
        \item Designed and wrote a multi-threaded server to facilitate multi-player communications.
        \item Managed multiple team members to efficiently work towards project goals.
    }

    \project{VirtualMachine}{ECS 150: Operating Systems}{01/15 -- 03/15}{
        \item Implemented a preemptive multitasking scheduler.
        \item Implemented blocking file access through use of asynchronous I/O on shared memory.
        \item Partially implemented access to a FAT file system image.
	}

\section{SKILLS}
	\vspace{2mm}
	%\begin{center}
	\begin{tabularx}{\textwidth}{|X|X|X|X|}
		\hline		
		Exposed & Familiar & Proficient & Advanced \\ \hline
		Lisp, Prolog, System Verilog, Vagrant &
		JavaScript, R, SQL, LaTex, OpenCV, gdb, ctags, Maven, WireShark &
		Python, Java, ssh, git, bash, Make, Vim, Eclipse, Virtualbox &
		C, C++ \\
		\hline
	\end{tabularx} \\
	%\end{center}

%	Proficient:
%	\begin{itemize}[noitemsep]
%	    \item[] {\sl Programming Languages:}  C, C++, Java, JavaScript, Python
%	    %\item[] {\sl Operating Systems:} Debian, Ubuntu, Linux Mint, Arch Linux, Windows XP -- Windows 10
%    	%\item[] {\sl Software Engineering:} bash, ssh, git, make, Maven, LaTex, PostgresSQL
%    	%\item[] {\sl Misc Technologies:} bash, ssh, LaTeX, PostgreSQL 
%    	%\item[] {\sl Useful Applications:} VirtualBox, Vim, Eclipse, Wireshark 
%    	%\item[] {\sl Miscellaneous: } bash, ssh, gdb, Git, Make, OpenCV, VirtualBox, Wireshark
%    	\item[] bash, ssh, gdb, Git, Make
%    	\item[] VirtualBox, Vagrant, Wireshark
%	\end{itemize} \vspace{-4mm} 
%    Familiar
%	\begin{itemize}[noitemsep]
%		\item[] SQL, LaTex, OpenCV, gdb, ctags
%		\item[] Maven, Vim, Eclipse, 
%	\end{itemize} \vspace{-4mm} 
%    Exposed
%	\begin{itemize}[noitemsep]
%    	\item[] Lisp, Prolog, Verilog, Scheme
%	\end{itemize} \vspace{-4mm}

% C, C++, Java, JavaScript, Python, Debian, Ubuntu, Linux Mint, Arch Linux, Windows XP -- Windows 10, bash, ssh, make, Maven, LaTex, PostgreSQL, SQL, VirtualBox, Vim, Eclipse, Wireshark, gdb, OpenCV, VirtualBox, Vagrant, ctags, Lisp, Prolog, System Verilog, Scheme


%\section{COURSEWORK}
%    ECS 20 - Discrete Mathematics \\
%    ECS 30 - Introduction to Programming (in C) \\
%    ECS 40 - Software Development and Object-Oriented Programming (in C++) \\
%    ECS 50 - Assembly Languages \\
%    ECS 60 - Data Structures and Algorithms \\
%    ECS 122A - Algorithm Analysis and Design \\
%    ECS 132 - Probability and Statistics \\
%    ECS 140 - Programming Languages \\
%    ECS 150 - Operating Systems \\
%    ECS 152A - Computer Networks \\
%    ECS 160 - Software Engineering \\
%    ECS 171 - Machine Learning \\
%    ECS 154A/B - Computer Architecture \\
%    ECS 193A/B - Senior Design \\

%\section{EXTRA-CURRICULAR ACTIVITIES}
%    Senator, Black Engineers Association (UC Davis chapter of NSBE) \hfill {\bf 01/12 -- Present} \\
%    Member, Black Engineers Association (UC Davis chapter of NSBE) \\
%    Member, Computer Science Club \\
%    Member, Linda Francis Alexander Scholars \\
%
%\section{COMMUNITY}
%    {\bf Teacher}, Educating Young Minds \hfill {\bf 06/13 -- 08/13} \\
%    |\raggedright{\hfill {\bf 06/12 -- 08/12}} \\
%    Los Angeles, CA
%    \begin{itemize} \itemsep -2pt
%        \item Taught grammar, reading comprehension, and essay-writing skills to classes between 5th and 12th grade.
%    \end{itemize}
%
%    {\bf Camp Counselor}, Jenesse, Women's Shelter \hfill {\bf 07/11 -- 08/11} \\
%    Los Angeles, CA
%    \begin{itemize} \itemsep -2pt % Reduce space between items
%        \item Supervised children at summer camp; chaperoned on Friday outings.
%    \end{itemize}

%---------------------------------------------------------------------------------------------------

\end{resume}
\end{document}
