\documentclass[line, letterpaper]{res}

%\usepackage{showframe}
\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{fancyhdr} % Using to edit header/footer
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX

% Put things in the headers/footers
\fancypagestyle{plain}{
    \fancyhf{} % No page number. (Don't ask me why.)

    \rfoot{Compiled on {\mmddyyyydate\today} at \currenttime}
}
%\pagestyle{plain} % apply style described above

\begin{document}
\name{Joseph Marvin McGee}
\address{jmmcgee@ucdavis.edu | (323) 557-8647}

\begin{resume}
%---------------------------------------------------------------------------------------------------

%\section{OBJECTIVE}
%    Seeking a career that will help me take full advantage of my passion and experience in software engineering and computer science. 

\vspace{-5mm}
\section{EDUCATION}
    {\sl Bachelor of Computer Science and Engineering}, (expected June 2016) \\
    University of California, Davis, California \\
%    Relevant Coursework:
%    \begin{itemize}
%        \item Data Structures
%        \item Assembly Languages
%        \item Computer Architecture
%        \item Programming Languages
%        \item Probability and Statistics.
%        \item Algorithms
%        \item 
%        \item Senior Design
%    \end{itemize}
    Cumulative GPA: \quad 3.114/4.000 (Overall) \quad 3.667/4.000 (Major)

\section{TECHNOLOGY \\ SKILLS} 
    {\sl Programming Languages:}  C, C++, Java, JavaScript, Python \\
    {\sl Web Technologies:} Django, Vaadin, NodeJS, JQuery \\
    {\sl Software Engineering:} Git, Maven, GNU Make \\
    {\sl Misc. Technologies:} bash, ssh, LaTeX, MinGW, PostgreSQL, VirtualBox \\
    {\sl Environments:} Vim, Code Blocks, Visual Studios, Eclipse \\
    {\sl Operating Systems:} Debian, Ubuntu, Windows XP -- Windows 8.1

\section{EXPERIENCE}
    {\bf Student Manager}, Engineering Student Startup Center \hfill {\bf 10/13 - Present} \\
    University of California, Davis
    \begin{itemize} \itemsep -2pt % Reduce space between items
        \item Created simple scripts to manage event-scheduling and forms management.
        \item Assisted students with equipment: 3D Printer, 3D Scanner, ShopBot.
        \item Acted as primary editor for website.
        \item Planned and facilitated events; Coordinated with student-run organizations.
    \end{itemize}

    {\bf Co-Founder and Software Engineer}, Archer \hfill {\bf 05/13 - Present} \\
    Davis, CA
    \begin{itemize} \itemsep -2pt % Reduce space between items
        \item Designed computer vision algorithms to facilitate a spatial input mechanism.
        % gap between increasingly complex media delivery systems and a stagnated input interface---the remote control.
        \item Engineered prototype under time-pressure to show progress to potential investors.
        %We recently incorporated and are developing our prototype and showing it to potential investors.
        \item Designed and debugged systems to visualize and quantify correctness of algorithm output.
        %I am responsible for is designing, coding and testing the prototype.
    \end{itemize}
    
    {\bf Software Engineer (Intern)}, Intel, Jones Farms Campus \hfill {\bf 06/14 - 09/14} \\
    Hillsboro, OR
    \begin{itemize} \itemsep -2pt
        \item Interpreted broad project requirements to create specific designs.
        \item Engineered and configured a functional database-centered web application.
            \subitem -- Identified and addressed concurrency issues with the system.
            \subitem -- Documented progress and kept records of code history in Git.
        \item Presented design goals and realized solution for Team to actual use.
        
    \end{itemize}

    {\bf Teacher}, Educating Young Minds \hfill {\bf 06/13 - 08/13} \\
    |\raggedright{\hfill {\bf 06/12 - 08/12}} \\
    Los Angeles, CA
    \begin{itemize} \itemsep -2pt
        \item Taught grammar, reading comprehension, and essay-writing skills to classes between 5th and 12th grade.
    \end{itemize}

    {\bf Camp Counselor} Jenesse, Women's Shelter \hfill {\bf 07/11 - 08/11} \\
    Los Angeles, CA
    \begin{itemize} \itemsep -2pt % Reduce space between items
        \item Supervised children at summer camp.
        \item Chaperoned on Friday outings.
    \end{itemize}

\section{EXTRA-CURRICULAR ACTIVITIES}     
    Member, Black Engineers Association \\
    Member, Computer Science Club \\
    Member, Linda Francis Alexander Scholars \\
 
%---------------------------------------------------------------------------------------------------

\end{resume}
\end{document}
